### 2017-11-11 vipassana-for-hackers.tex
fixing warnings in bibliography

\setlength{\parindent}{2em}
\setlength{\parskip}{0.7em}
\setlist{noitemsep}

@@

Consider this warning to also extend to any literature which \textbf{does} attempt to convey Vipassana meditation instruction. Specifically, Glickman's \textit{Beyond the Breath: Extraordinary Mindfulness Through Whole-Body Vipassana Meditation} \cite{glickman} includes a facsimile of instruction provided on a 10-day introductory Vipassana course. Instruction on a course includes 11+ hours of video instruction, at least twice as many hours of audio instruction, and multiple interviews per day with the teacher. Trying to replace this with a book is both inadequate and dangerous.\\

@@

I should note that I have never successfully penetrated my muscles or inner tissues much. The average new meditator is likely to feel a great many fascinating sensations on her fingertips, palms, arms, toes, and legs. The torso, since it is surrounded in longer nerve fibres, will take longer to observe in the same way. \textit{[citation needed]}\\

@@

The autonomic nervous system is what causes the ``winding stack'' of thought and emotion described earlier. The autonomic nervous system is what makes --- and keeps --- you angry. And afraid. And sad. And anxious. And everything else you feel.

@@

\begin{itemize}
\item \textit{The Art of Living: Vipassana Meditation As Taught by S. N. Goenka} (Hart, 1987)
\item \textit{An Atheist's Glimpse of God}, my write-up of my first 10-Day Vipassana course:
  \begin{itemize}
  \item \url{http://blog.deobald.ca/2013/02/an-atheists-glimpse-of-god.html}
  \end{itemize}
\item \textit{Drugs, meditation, warnings}, my comparison of meditation techniques and various drugs:
  \begin{itemize}
  \item \url{http://blog.deobald.ca/2015/01/drugs-meditation-warnings.html}
  \end{itemize}
\end{itemize}

@@

\begin{thebibliography}{9}
\bibitem{thenewsroom}
  Aaron Sorkin.
  \url{https://www.youtube.com/watch?v=2C6h-Yyx9Yk}
  \textit{The Newsroom}.
  HBO, 2012.

>>>>

\setlength{\parindent}{1.3em}
\setlength{\parskip}{0.7em}
\setlist{noitemsep}

@@

Consider this warning to also extend to any literature which \textbf{does} attempt to convey Vipassana meditation instruction. Specifically, Glickman's \textit{Beyond the Breath: Extraordinary Mindfulness Through Whole-Body Vipassana Meditation} \cite{glickman} includes a facsimile of instruction provided on a 10-day introductory Vipassana course. Instruction on a course includes 11+ hours of video instruction, at least twice as many hours of audio instruction, and multiple interviews per day with the teacher. Trying to replace this with a book is both inadequate and dangerous.

@@

I should note that I have never successfully penetrated my muscles or inner tissues much. The average new meditator is likely to feel a great many fascinating sensations on her fingertips, palms, arms, toes, and legs. The torso, since it is surrounded in longer nerve fibres, will take longer to observe in the same way. \textit{[citation needed]}

@@

The autonomic nervous system is what causes the ``winding stack'' of thought and emotion described earlier. The autonomic nervous system is what makes (and keeps) you angry. And afraid. And sad. And anxious. And everything else you feel.

@@

\begin{itemize}
\item \textit{The Art of Living: Vipassana Meditation As Taught by S. N. Goenka} (Hart, 1987)
\item \textit{An Atheist's Glimpse of God}, my write-up of my first 10-Day Vipassana course:
  \begin{itemize}
  \item \href{http://blog.deobald.ca/2013/02/an-atheists-glimpse-of-god.html}
             {\nolinkurl{http://blog.deobald.ca/2013/02/}}\\
        \href{http://blog.deobald.ca/2013/02/an-atheists-glimpse-of-god.html}
             {\nolinkurl{an-atheists-glimpse-of-god.html}}
  \end{itemize}
\item \textit{Drugs, meditation, warnings}, my comparison of meditation techniques and various drugs:
  \begin{itemize}
  \item \href{http://blog.deobald.ca/2015/01/drugs-meditation-warnings.html}
             {\nolinkurl{http://blog.deobald.ca/2015/01/}}\\
        \href{http://blog.deobald.ca/2015/01/drugs-meditation-warnings.html}
             {\nolinkurl{drugs-meditation-warnings.html}}
  \end{itemize}
\end{itemize}

@@

\begin{thebibliography}{9}
\raggedright

\bibitem{thenewsroom}
  Aaron Sorkin.
  \url{https://www.youtube.com/watch?v=2C6h-Yyx9Yk}
  \textit{The Newsroom}.
  HBO, 2012.
